---
title: "Happiness and Meaning Data Analysis"
author: "Rhia Catapano"
date: "March 18, 2016"
output: html_document
---

```{r, echo=FALSE, message=FALSE}
library(ggplot2)
library(reshape2)
library(knitr)
library(dplyr)
```

```{r, message=FALSE, warning=FALSE}
m_h_dat <- read.csv("https://raw.githubusercontent.com/joelcarlson/ForRhia/master/RhiaMeaningHappMar17.csv")
#Drop the attention check answers to lowercase
m_h_dat$What.company.was.the.advertisement.for. <- tolower(m_h_dat$What.company.was.the.advertisement.for.)

#Filter out anyone who didnt say either chrome, gmail, or google somewhere in their answer
m_h_dat_attn_pass <- filter(m_h_dat, grepl("chrome", What.company.was.the.advertisement.for.) |
                                      grepl("gmail", What.company.was.the.advertisement.for.)  |
                                      grepl("google", What.company.was.the.advertisement.for.))

#Remove attention check column
m_h_dat <- select(m_h_dat, -What.company.was.the.advertisement.for.)
m_h_dat_attn_pass <- select(m_h_dat_attn_pass, -What.company.was.the.advertisement.for.)

m_h_melt <- melt(m_h_dat)


ggplot(data=m_h_melt, aes(x=variable, y=value, fill=Condition)) + geom_boxplot()+
  ggtitle("All Participants \n (Median as center line)")
```

This graph is indeed correct, as bizarre as it looks. A boxplot does not show the mean within groups, it shows the median. As we can see below, the medians for each group are identical:

```{r}
kable(m_h_melt %>% group_by(Condition, variable) %>% summarize(median(value), mean(value)))
```

If we really want to see the means in the boxplot then we can do a little work:

```{r}
mean_bp_dat <- m_h_melt %>% group_by(Condition, variable) %>% summarize(ymin=min(value),
                                                         y25=quantile(value,0.25),
                                                         ymean=mean(value),
                                                         y75=quantile(value,0.75),
                                                         ymax=max(value))
ggplot(data=mean_bp_dat, aes(x=variable)) +
  geom_boxplot(
    aes(ymin = ymin, lower = y25, middle = ymean, upper = y75, ymax = ymax, fill=Condition),
    stat = "identity"
  ) +
  ggtitle("All Participants\n (Mean as center line)")
```

##Statistical Significance

Assuming you are wanting to use t-tests:

```{r}
get_t_test <- function(data, ref, target, column, digits=3){
  t_test <- t.test(filter(data, Condition == ref)[[column]], 
                   filter(data, Condition == target)[[column]])
  list("ref" = ref,
       "target" = target,
       "ref_mean"  = round(unname(t_test$estimate[1]),digits),
       "target_mean"  = round(unname(t_test$estimate[2]),digits),
       "mean_diff"= round(unname(diff(t_test$estimate)),digits),
       "p"        = round(t_test$p.value,digits),
       "lower"    = round(t_test$conf.int[1],digits),
       "upper"    = round(t_test$conf.int[2],digits)
       )
}

t_happiness <- list(
  get_t_test(data=m_h_dat, ref="nonparents1", target="nonparents2", column="Rate.Happiness."),
  get_t_test(data=m_h_dat, ref="nonparents1", target="parents", column="Rate.Happiness."),
  get_t_test(data=m_h_dat, ref="nonparents2", target="parents", column="Rate.Happiness.")
)

t_meaning <- list(
  get_t_test(data=m_h_dat, ref="nonparents1", target="nonparents2", column="Rate.Meaningfulness."),
  get_t_test(data=m_h_dat, ref="nonparents1", target="parents", column="Rate.Meaningfulness."),
  get_t_test(data=m_h_dat, ref="nonparents2", target="parents", column="Rate.Meaningfulness.")
)
```

###Happiness

```{r}
kable(do.call(rbind.data.frame, t_happiness))
```

###Meaningfulness

```{r}
kable(do.call(rbind.data.frame, t_meaning))
```


#Do it all over again with the people who passed the attention check!

There are `r nrow(m_h_dat_attn_pass)` participants who passed the attn check.

```{r, message=FALSE, error=FALSE, echo=FALSE}
m_h_melt_attn_pass <- melt(m_h_dat_attn_pass)
ggplot(data=m_h_melt_attn_pass, aes(x=variable, y=value, fill=Condition)) + geom_boxplot()+
  ggtitle("Participants who Passed Attn. Check \n (Median as center line)")


kable(m_h_melt_attn_pass %>% group_by(Condition, variable) %>% summarize(median(value), mean(value)))

mean_bp_dat_attn_pass <- m_h_melt_attn_pass %>% 
  group_by(Condition, variable) %>% 
  summarize(ymin=min(value),
            y25=quantile(value,0.25),
            ymean=mean(value),
            y75=quantile(value,0.75),
            ymax=max(value))

ggplot(data=mean_bp_dat_attn_pass, aes(x=variable)) +
  geom_boxplot(
    aes(ymin = ymin, lower = y25, middle = ymean, upper = y75, ymax = ymax, fill=Condition),
    stat = "identity"
  ) +
  ggtitle("Participants who Passed Attn. Check \n (Mean as center line)")
```

##Statistical Significance 
###(Participants who passed attn check)


```{r, echo=FALSE}
t_happiness <- list(
  get_t_test(data=m_h_dat_attn_pass, ref="nonparents1", target="nonparents2", column="Rate.Happiness."),
  get_t_test(data=m_h_dat_attn_pass, ref="nonparents1", target="parents", column="Rate.Happiness."),
  get_t_test(data=m_h_dat_attn_pass, ref="nonparents2", target="parents", column="Rate.Happiness.")
)

t_meaning <- list(
  get_t_test(data=m_h_dat_attn_pass, ref="nonparents1", target="nonparents2", column="Rate.Meaningfulness."),
  get_t_test(data=m_h_dat_attn_pass, ref="nonparents1", target="parents", column="Rate.Meaningfulness."),
  get_t_test(data=m_h_dat_attn_pass, ref="nonparents2", target="parents", column="Rate.Meaningfulness.")
)
```

###Happiness

```{r, echo=FALSE}
kable(do.call(rbind.data.frame, t_happiness))
```

###Meaningfulness

```{r, echo=FALSE}
kable(do.call(rbind.data.frame, t_meaning))
```

